---
title: "Deli4Test"
---

## Deliverable 4

First, we'll load in our Real Estate cleaned/formatted data set from Github.

```{r}
library(dplyr)
library(tidyverse)
```

```{r}
real_estate_link = "https://github.com/DataPreProcessing-FALL2024/Deli2Test/raw/refs/heads/main/DataCleanAndFormatted/Formatted_Real_Estate_Data.RDS"

real_estate_data = readRDS(gzcon(url(real_estate_link)))
head(real_estate_data)
```

Now, we will select only some columns of interest to keep for future aggregation.

```{r}
real_estate_data <- real_estate_data %>%
  select(size_sqft, price_bdt, year_built, 
         building_registration_type, furnished, location)
```

### Aggregation

#### 1 Group, 1 Function, 1 Input Variable

Mean square footage by location

```{r}
squarefootMeanByLocation = 
  aggregate(data = real_estate_data, size_sqft ~ location,
            function(x) mean = mean(x))

squarefootMeanByLocation
```

Now, we'll save this resulting aggregation to an RDS file.

```{r}
folder = "finalOutput"

# Check if the folder exists
if (!dir.exists(folder)) {
  # Create the folder
  dir.create(folder)
  saveRDS(squarefootMeanByLocation,file.path(folder,"output111.rds"))

} else {
  saveRDS(squarefootMeanByLocation,file.path(folder,"output111.rds"))

}
```

#### 2 Groups, 2 Functions, 1 Input Variable

Mean and median price by location and whether or not it's furnished

```{r}
priceMeanMedianByLocationAndFurnished = aggregate(
  data = real_estate_data, price_bdt ~ location + furnished,
  function(x) c(mean = mean(x), median = median(x)))

priceMeanMedianByLocationAndFurnished
```

Now, we'll save the resulting aggregation to an RDS file.

```{r}
folder = "finalOutput"

# Check if the folder exists
if (!dir.exists(folder)) {
  # Create the folder
  dir.create(folder)
  saveRDS(priceMeanMedianByLocationAndFurnished,file.path(folder,"output221.rds"))

} else {
  saveRDS(priceMeanMedianByLocationAndFurnished,file.path(folder,"output221.rds"))

}
```

#### 1 Group, 2 Input Variables, Different Function For Each

Mean price and median square footage by year built

```{r}
meanPricemedianSqftByYear = real_estate_data %>%
  group_by(year_built) %>%
  summarize(pricebdt_mean = mean(price_bdt),
            sizesqft_median = median(size_sqft))

meanPricemedianSqftByYear
```

Now, we'll save the resulting aggregation to an RDS file.

```{r}
folder = "finalOutput"

# Check if the folder exists
if (!dir.exists(folder)) {
  # Create the folder
  dir.create(folder)
  saveRDS(meanPricemedianSqftByYear,file.path(folder,"output111.rds"))

} else {
  saveRDS(meanPricemedianSqftByYear,file.path(folder,"output12f1f2.rds"))

}
```
